Sound and Automated Synthesis of Digital Stabilizing Controllers for Continuous Plants \thanks{Supported by EPSRC grant EP/J012564/1, ERC project 280053 (CPROVER) and the H2020 FET OPEN SC$^2$.}

### 2017-02-15 hscc2017/paper.tex
wording

Uncertainties in $G(z)$ may appear due to: 
1. uncertainties in $G(s)$ (we denote the uncertain continuous plant by $\hat{G}(s)=\frac{G_n(s)+\Delta_p{G}_n(s)}{G_d(s)+\Delta_p{G}_d(s)}$ to explicitly encompass the effects of the uncertainty terms $\Delta_p{G}_{(\cdot)}(s)$) arising from tolerances/imprecision in the original model; 
2. errors in the numerical calculations due to FWL effects (e.g., coefficient truncation and round-off, which will be denoted as $\Delta_b{G}_n(s),\Delta_b{G}_d(s)$);    
and 
3. errors caused by quantization (which we model later as as external disturbances $\nu_1$ and $\nu_2$). 
These uncertainties are parametrically expressed by additive terms, eventually resulting in an uncertain model $\hat{G}(z)$, such that:
%
\begin{equation}
\hat{G}(z)=\frac{G_n(z)+\Delta G_n(z)}{G_d(z)+\Delta G_d(z)},
\end{equation}
%
%\red{[what is the relationship between the deltas in this formula, and those in the previous paragraph? please clarify and hopefully simplify formulae. ]}
which will be represented by the following transfer function:
%
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}. 
\end{equation}
%
%\red{[why is this condition on the order of the polynomials raised only now? how is it used later?]}
Notice that, due to the nature of the methods we use for the stability check, we require
that the parametric errors in the plant have the same polynomial order as
the plant itself (indeed, all other errors described in this paper are ensured to
fulfil this property in our implementation). 
We also remark that, due to its native digital implementation, 
there are no parametric errors ($\Delta_pC_n(z), \Delta_pC_d(z)$) entering in the controller. 
Thus $\hat{C}(z) \equiv C(z)$.

>>>>

Uncertainties in $G(z)$ may appear owing to: 1.~uncertainties in $G(s)$ (we
denote the uncertain continuous plant by
$\hat{G}(s)=\frac{G_n(s)+\Delta_p{G}_n(s)}{G_d(s)+\Delta_p{G}_d(s)}$ to
explicitly encompass the effects of the uncertainty terms
$\Delta_p{G}_{(\cdot)}(s)$) arising from tolerances/imprecision in the
original model; 2.~errors in the numerical calculations due to FWL effects
(e.g., coefficient truncation and round-off, which will be denoted as
$\Delta_b{G}_n(s),\Delta_b{G}_d(s)$); and 3.~errors caused by quantization
(which we model later as as external disturbances $\nu_1$ and $\nu_2$). 
These uncertainties are parametrically expressed by additive terms,
eventually resulting in an uncertain model $\hat{G}(z)$, such that:
%
\begin{equation}
\hat{G}(z)=\frac{G_n(z)+\Delta G_n(z)}{G_d(z)+\Delta G_d(z)},
\end{equation}
%
%\red{[what is the relationship between the deltas in this formula, and those in the previous paragraph? please clarify and hopefully simplify formulae. ]}
which will be represented by the following transfer function:
%
\begin{equation}
\hat{G}(z)=\frac{\hat{b}_{0}+\hat{b}_{1}z^{-1}+...+\hat{b}_{M_G}z^{-M_G}}{\hat{a}_{0}+\hat{a}_{1}z^{-1}+...+\hat{a}_{N_G}z^{-N_G}}. 
\end{equation}
%
%\red{[why is this condition on the order of the polynomials raised only
now?  how is it used later?]} Notice that, due to the nature of the methods
we use for the stability check, we require that the parametric errors in the
plant have the same polynomial order as the plant itself (indeed, all other
errors described in this paper fulfil this property).  We
also remark that, due to its native digital implementation, there are no
parametric errors ($\Delta_pC_n(z), \Delta_pC_d(z)$) entering in the
controller.  Thus $\hat{C}(z) \equiv C(z)$.
